Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-15 doc/JFLA2022/Slides/Slides.tex
Slides (small changes)

 {\color{mathcolor}
\begin{align}
  H'_0(i) & = i\\
  H'_{\beta+1}(i) &=H'_\beta(i+1) \\
  H'_\lambda(i) &= H'_{(\canonseq{\lambda}{i+1})}(i)  \quad\textit{($\lambda$ limit ordinal)} 
\end{align}}

\textcolor{mathcolor}{$H'_\alpha(i)$} is the least $l$ such that \textcolor{mathcolor}{$\alpha_l=0$} (cf. previous slide)).

@@

{\color{mathcolor}
\begin{align}
F_0(i)& =i+1\\
F_{\beta+1}(i)&= (F_\beta)^{(i+1)}(i)\\
F_\lambda(i) &= F_{(\canonseq{\lambda}{i})} (i) \quad \textit{($\lambda$ limit ordinal)}
\end{align}}}
\end{block}
\end{frame}

@@

  \begin{block}{Theorems}
    \begin{itemize}
    \item $F_\alpha$ is primitive recursive iff $\alpha<\omega$.
     \item  
    The function which computes the length of hydra battles
    for $\alpha$ (according to the initial index) is not primitive recursive
    (for $\alpha\geq \omega^\omega$).

    \end{itemize}

>>>>

 \textbf{Definition:} \textcolor{mathcolor}{$H'_\alpha(i)$} is the least $l$ such that \textcolor{mathcolor}{$\alpha_l=0$} (cf. previous slide).

 {\color{mathcolor}
\begin{align}
  H'_0(i) & = i\\
  H'_{\beta+1}(i) &=H'_\beta(i+1) \\
  H'_\alpha(i) &= H'_{(\canonseq{\alpha}{i+1})}(i)  \quad\textit{($\alpha$ limit ordinal)} 
\end{align}}

@@

{\color{mathcolor}
\begin{align}
F_0(i)& =i+1\\
F_{\beta+1}(i)&= (F_\beta)^{(i+1)}(i)\\
F_\alpha(i) &= F_{(\canonseq{\alpha}{i})} (i) \quad \textit{($\alpha$ limit ordinal)}
\end{align}}}
\end{block}
\end{frame}

@@

  \begin{block}{Theorems}
    \begin{itemize}
    \item \textcolor{mathcolor}{$F_\alpha$} is primitive recursive iff \textcolor{mathcolor}{$\alpha<\omega$}.
     \item  
    The function which computes the length of hydra battles
    for \textcolor{mathcolor}{$\alpha$} (according to the initial index) is not primitive recursive
    (for $\textcolor{mathcolor}{\alpha\geq \omega^\omega}$).
    \end{itemize}
